---
title: "Sorites Data Summary"
author: "Erin Bennett"
output: "pdf_document"
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo=F, warning=F, cache=F, message=F, sanitiz=F, fig.width = 5, fig.height = 3)
```

```{r}
source("~/Settings/startup.R")
library(knitr)
library(pander)
```

## Wording used in Sorites experiments

```{r}
sorites_designs = read.csv("data/sorites/sorites_designs.csv")
sorites_designs %>%
  select(-prompt, -left, -right, -concrete, -inductive) %>%
  rename(`inductive phrasing` = inductive_label) %>%
  pander(.,
       caption="Sorites variations",
       align=rep("l", ncol(sorites_designs)))
lookup_phrasing = function(inductive_phrasing) {
  return((
    sorites_designs %>%
      filter(inductive_label==inductive_phrasing)
  )$inductive[[1]])
}
```

Possible phrasings of inductive premise:

* relative: "`r lookup_phrasing("relative")`"
* conditional: "`r lookup_phrasing("conditional")`"

Consistent across all experiments:

* Concrete premise: "`r sorites_designs$concrete[[1]]`"
* Prompt: "`r sorites_designs$prompt[[1]]`"
* Left (lower) label of likert scale: "`r sorites_designs$left[[1]]`""
* Right (higher) label of likert scale: "`r sorites_designs$right[[1]]`""

*In experiments 7a and 7b, phrasing was randomized between participants (either relative or conditional), but I did not record which phrasing was used for which participant

