---
title: "Sorites Experiment 6"
output:
  pdf_document:
    toc: true
    highlight: zenburn
    toc_depth: 3
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
  echo=F, warning=F, #cache=T, 
  message=F, #sanitiz =T, 
  fig.width = 5, fig.height = 3)
```


```{r load libraries, echo=F, message=F, warning=F}
library(rjson)
library(fitdistrplus)
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
library(grid)
library(ggthemes)
library(languageR)
library(psych)
library(lme4)
library(lmerTest)
library(diagram)
library(boot)
char = as.character
num = function(x) {return(as.numeric(char(x)))}
grab = function(colname) { return(function(lst) { return(unlist(lst[[colname]])) }) }
options(digits=3)
mean.sd = funs(mean, sd)
samplemean <- function(x, d) {
  return(mean(x[d]))
}
ci = function(vals) {
  if(length(vals)<2) {return(data.frame(mean=mean(vals), ci.low=NA, ci.high=NA, N=length(vals)))}
  cis = boot.ci(boot(vals, samplemean, 1000), type="bca")
  low = cis$bca[1,4]
  high = cis$bca[1,5]
  return(data.frame(mean=mean(vals),
                    ci.low=low,
                    ci.high=high,
                    N=length(vals)))
}
```

## Description of experiment

A copy of the "prior" version of this experiment can be found at [`experiments/experiment6-conditionA/morebins.html`](../experiments/experiment6-conditionA/morebins.html), and a copy of the "posterior" version of this experiment can be found at [`experiments/experiment6-conditionB/morebins.html`](../experiments/experiment6-conditionB/morebins.html).

This was the fourth binned prior elicitation experiment that I worked on, which we ran in December of 2013 and January of 2014. The design was identical to Experiments [3](experiment3.pdf), [4](experiment4.pdf), and [5](experiment5.pdf), except that the number of bins varied by item and we included a "posterior" condition in which the item was labeled "expensive".

There were 30 participants in this version, 10 in the prior condition and 20 in the posterior condition

```{r load data, echo=F, warning=F, message=F}
# ## combine two data files together:
# d0.raw = read.csv('../data/experiment5-and-experiment6.csv') %>%
#   filter(workerid >= 10) %>%
#   mutate(condition = ifelse(workerid < 20, 'prior', 'posterior')) %>%
#   mutate(workerid = factor(workerid)) %>%
#   rename(language=Answer.language,
#          age=Answer.age,
#          comments=Answer.comments) %>%
#   mutate(language = factor(sub('"', '', sub('"', '', char(language))))) %>%
#   select(workerid, Answer.0,
#          Answer.1, Answer.2,
#          Answer.3, Answer.4, condition) %>%
#   gather('qnumber', 'question.data', 2:6) %>%
#   mutate(qnumber = sapply(.$qnumber, function(q) {return(substring(q, 8))}),
#          qnumber = num(qnumber),
#          qtype = ifelse(qnumber < 5, 'bins', 'max'))
#          
# ## extract lame data collection into long form
# d0 = ldply(lapply(1:nrow(d0.raw), function(i) {
#   question.data = fromJSON(d0.raw[i, 'question.data'])
#   qtype = d0.raw[i, 'qtype']
#   if (qtype == 'bins') {
#     workerid = d0.raw[i, 'workerid']
#     qnumber = d0.raw[i, 'qnumber']
#     condition = d0.raw[i, 'condition']
#     item = question.data$item
#     response = question.data$responses
#     lower = question.data$lowers
#     upper = unname(unlist(question.data$uppers))
#   } else {
#     workerid = d0.raw[i, 'workerid']
#     qnumber = d0.raw[i, 'qnumber']
#     condition = d0.raw[i, 'condition']
#     item = question.data$item
#     response = question.data$response
#     lower = NA
#     upper = NA
#   }
#   return(data.frame(workerid=workerid,
#                     qnumber=qnumber,
#                     qtype=qtype,
#                     condition = condition,
#                     item=item,
#                     response=response,
#                     lower=lower,
#                     upper=upper))
# }), rbind)
# # write.csv(d0, "../data/experiment6-processed.csv", row.names=F)
d0 = read.csv("../data/experiment6-processed.csv")
```

## Results

Some version of these results inspired the mean and standard deviations that we used in [Experiment 7](experiment7.pdf).

```{r plotdensities, echo=F, message=F, warning=F, fig.width=8, fig.height=3}
aggr = d0 %>% filter(qtype == 'bins') %>%
  group_by(condition, item, workerid) %>%
  mutate(normed.response = response / sum(response)) %>%
  as.data.frame %>%
  group_by(condition, item, lower, upper) %>%
  do(ci(.$normed.response)) %>%
#   summarise(mean = mean(normed.response)) %>%
  rename(response=mean) %>% as.data.frame

ggplot(aggr, aes(x=lower, y=response, colour=item, fill=item)) +
#   geom_bar(stat='identity') +
  geom_line() +
  geom_ribbon(aes(ymin=ci.low,ymax=ci.high),alpha=0.5,lwd=0) +
  facet_grid(condition~item, scale='free') +
  theme_few() + scale_colour_few() + scale_fill_few()

aggr %>% group_by(item) %>% filter(condition=='prior') %>%
  mutate(upper = num(gsub('infty', 'NaN', char(upper)))) %>%
  filter(!is.nan(upper)) %>%
  summarise(mean=sum(response*(lower+upper)/2),
            sd = sqrt(sum(((lower+upper)/2-mean)^2)/(length(response)-1))) %>%
  as.data.frame
```

