---
title: "Sorites Experiment 8"
output:
  pdf_document:
    toc: true
    highlight: zenburn
    toc_depth: 3
---

```{r load libraries, echo=F, message=F, warning=F}
library(rjson)
library(fitdistrplus)
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
library(grid)
library(ggthemes)
library(languageR)
library(psych)
library(lme4)
library(lmerTest)
library(diagram)
library(boot)
char = as.character
num = function(x) {return(as.numeric(char(x)))}
grab = function(colname) { return(function(lst) { return(unlist(lst[[colname]])) }) }
options(digits=3)
mean.sd = funs(mean, sd)
samplemean <- function(x, d) {
  return(mean(x[d]))
}
ci = function(vals) {
  if(length(vals)<2) {return(data.frame(mean=mean(vals), ci.low=NA, ci.high=NA, N=length(vals)))}
  cis = boot.ci(boot(vals, samplemean, 1000), type="bca")
  low = cis$bca[1,4]
  high = cis$bca[1,5]
  return(data.frame(mean=mean(vals),
                    ci.low=low,
                    ci.high=high,
                    N=length(vals)))
}
```

## Description of experiment

This was a prior elicitation experiment with bins in which we had two presentation conditions: the original presentation condition, where all of the bins for an item were presented at once, in sequence from left to right, and a new condition where each bin was asked about on its own slide. The resolution was relatively low and varied by item. A copy of the experiment can be found at [`experiments/experiment8/morebins.html`](../experiments/experiment8/morebins.html).

There were N participants in this version, N in the prior condition and N in the posterior condition.

```{r load data, echo=F, warning=F, message=F}
## combine two data files together:
d0.raw = read.csv('../data/experiment8.csv') %>%
  mutate(workerid = factor(workerid)) %>%
  rename(language=Answer.language,
         age=Answer.age,
         comments=Answer.comments,
         presentation.condition=Answer.cond) %>%
  mutate(language = factor(sub('"', '', sub('"', '', char(language)))),
         presentation.condition = factor(sub('"', '', sub('"', '', char(presentation.condition))))) %>%
  gather('qnumber', 'question.data', 31:66) %>%
  select(workerid, presentation.condition, qnumber, question.data) %>%
  mutate(qnumber = sapply(.$qnumber, function(q) {return(substring(q, 8))}),
         qnumber = num(qnumber))
         
## extract lame data collection into long form
d0 = ldply(lapply(1:nrow(d0.raw), function(i) {
  if (d0.raw[i, 'question.data'] == '') {
    return(data.frame(
      workerid = d0.raw[i, 'workerid'],
      qnumber = d0.raw[i, 'qnumber'],
      presentation.condition=d0.raw[i, 'presentation.condition'],
      item=NA,
      response=NA,
      lower=NA))}
  question.data = fromJSON(d0.raw[i, 'question.data'])
  presentation.condition = d0.raw[i, 'presentation.condition']
  if (presentation.condition == 'original') {
    workerid = d0.raw[i, 'workerid']
    qnumber = d0.raw[i, 'qnumber']
    item = question.data$item
    response = question.data$responses
    lower = question.data$lowers
    } else {
      workerid = d0.raw[i, 'workerid']
      qnumber = d0.raw[i, 'qnumber']
      item = question.data$item
      response = question.data$response
    lower = question.data$lower
  }
  return(data.frame(workerid=workerid,
                    qnumber=qnumber,
                    presentation.condition=presentation.condition,
                    item=item,
                    response=response,
                    lower=lower))
}), rbind)
```

## Results

The distributions elicited with bins split across trials were different. They were less peaky than the distributions elicited all at once.

```{r plotdensities, echo=F, message=F, warning=F, fig.width=8, fig.height=3}
aggr = d0 %>% filter(!is.na(response)) %>%
  group_by(presentation.condition, item) %>%
  mutate(normed.response = response / sum(response)) %>%
  as.data.frame %>%
  group_by(presentation.condition, item, lower) %>%
  do(ci(.$normed.response)) %>%
#   summarise(mean = mean(normed.response)) %>%
  rename(response=mean) %>% as.data.frame

ggplot(aggr, aes(x=lower, y=response, colour=presentation.condition, fill=presentation.condition)) +
#   geom_bar(stat='identity') +
  geom_line() +
  geom_ribbon(aes(ymin=ci.low,ymax=ci.high),alpha=0.5,lwd=0) +
  facet_grid(~item, scale='free') +
  theme_few() + scale_colour_brewer(type='qual') + scale_fill_brewer(type='qual')
```

```{r plotmax, echo=F, message=F, warning=F, fig.width=8, fig.height=3}
## plot max
```