---
title: "Sorites Experiment 10"
output:
  pdf_document:
    toc: true
    highlight: zenburn
    toc_depth: 3
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
  echo=F, warning=F, #cache=T, 
  message=F, #sanitiz =T, 
  fig.width = 5, fig.height = 3)
```

```{r load libraries, echo=F, message=F, warning=F}
library(rjson)
library(fitdistrplus)
library(ggplot2)
library(dplyr)
library(tidyr)
library(grid)
library(ggthemes)
library(languageR)
library(psych)
library(lme4)
library(lmerTest)
library(diagram)
library(boot)
char = as.character
num = function(x) {return(as.numeric(char(x)))}
grab = function(colname) { return(function(lst) { return(unlist(lst[[colname]])) }) }
options(digits=3)
mean.sd = funs(mean, sd)
# source("~/Settings/startup.R")
```

## Description of experiment

A copy of the experiment can be found at: [`experiments/experiment10/exp3-sorites.html`](../experiments/experiment10/exp3-sorites.html).

This was a sorites premises experiment that we ran in April of 2015. The design was the same as previous sorites experiments, but we asked about a wider range of epsilons and values. Using the previous experiments as pilots, we chose epsilons and values that we thought would elicit the full range of ratings.

```{r echo=F, fig.width=8, fig.height=2}
values = '{
  	"laptop": [350, 600, 900, 1250, 1850],
		"watch": [100, 250, 450, 900, 2000],
		"coffee maker": [24, 52, 84, 124, 188],
		"sweater": [18, 36, 57, 87, 150],
		"headphones": [24, 60, 96, 144, 234]
	}'
epsilons = '{
		"laptop": [18.50, 185.0, 925.0, 1295.0, 1850],
		"watch": [24.00, 240.0, 1200.0, 1680.0, 2400],
		"coffee maker": [2.00, 20.0, 100.0, 140.0, 200],
		"sweater": [1.71, 17.1, 85.5, 119.7, 171],
		"headphones": [2.58, 25.8, 129.0, 180.6, 258]
	}'
sorites.ranges = rbind(
  as.data.frame(fromJSON(values)) %>% gather('item', 'dollarAmt') %>% mutate(variable='value'),
  as.data.frame(fromJSON(epsilons)) %>% gather('item', 'dollarAmt') %>% mutate(variable='epsilon') )
sorites.ranges %>% ggplot(., aes(x=dollarAmt, y=variable, colour=item)) +
  geom_point() +
  facet_grid(~item, scale='free') +
  theme_few() + scale_colour_few()
```

For each of the 5 items, there were 5 possible concrete premise sentences and 5 possible inductive premise sentences. So each participant rating 50 sentences.

The inductive premise used the conditional statement phrasing.

## Results

There were 30 participants.

```{r, echo=F, message=F, warning=F, fig.width=8, fig.height=3}
# d0 = read.csv('../data/experiment10.csv') %>%
#   rename(questions=Answer.responses)
# d0 = d0[,c("workerid", "questions")]
# 
# questions = sapply(char(d0$questions), fromJSON)
# n0 = length(questions)
# nqns = nrow(questions)
# nsubj = ncol(questions)
# graball = function(colname) {
#   return(unlist(sapply(1:n0, function(i) {
#     return((grab(colname))(questions[[i]])) }))) }
# d0 = data.frame(qType = graball('qtype'),
#                 item = graball('object'),
#                 dollarAmt = graball('dollar_amount'),
#                 phrasing = graball('phrasing'),
#                 response = graball('response'),
#                 workerid = rep(d0$workerid, rep(nqns, length(d0$workerid)))) %>%
#   mutate(dollarAmt = as.numeric(sub('\\$','',as.character(dollarAmt))),
#          response = as.integer(response),
#          workerid = as.factor(workerid))
# 
# samplemean <- function(x, d) {
#   return(mean(x[d]))
# }
# ci = function(vals) {
#   cis = boot.ci(boot(vals, samplemean, 1000), type="bca")
#   low = cis$bca[1,4]
#   high = cis$bca[1,5]
#   return(data.frame(mean=mean(vals),
#                     ci.low=low,
#                     ci.high=high,
#                     N=length(vals)))
# }
# 
# aggr = d0 %>% group_by(item, dollarAmt, qType) %>%
# #   summarise(response = mean(response)) %>%
#   do(ci(.$response)) %>%
#   rename(response=mean) %>% as.data.frame
# ggplot(aggr, aes(x=dollarAmt, y=response, colour=item, linetype=qType)) +
#   geom_point() +
#   geom_line() +
#   geom_errorbar(aes(x=dollarAmt, ymin=ci.low, ymax=ci.high), width=0) +
#   facet_grid(~ item, scale='free') +
#   scale_y_continuous(breaks = 1:9, limits=c(1, 9)) +
#   theme_few() + scale_colour_few()
# # write.csv(d0, "../data/experiment10-processed.csv", row.names=F)
d0 = read.csv("../data/experiment10-processed.csv")
```

## Model fit (using Expt 9 priors)

```{r}
library(rwebppl)
library(tidyr)
library(dplyr)
# for bootstrapping 95% confidence intervals
theta <- function(x,xdata) {mean(xdata[x])}
ci.low <- function(x) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x)$thetastar,.025)}
ci.high <- function(x) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x)$thetastar,.975)}
```

```{r}
alpha = 5
cost = 6
priors_dir = "3domain-bins-priors"
model_commit = "315b4"
samples = 1000

if(priors_dir=="3domain-bins-priors") {
  relevant_items = c("laptop", "coffee maker", "watch")
} else {
  relevant_items = char(unique(d0$item))
}    

# adjectivesModel = function(listenerSamples, s1Samples) {
#   return(function(item){
#     rs = webppl(program_file = "adjectives-lognormal-prior.wppl",
#                 model_var = paste("adjectivesModel({",
#                                   "item: '", item, "', ",
#                                   "utterance: 'adjective', ",
#                                   "alpha: ", alpha, ",",
#                                   "cost: ", cost, ",",
#                                   "priors_dir: '", priors_dir, "',",
#                                   "inferenceOpts: {",
#                                   "listener: {method: 'MCMC', samples: ",
#                                   listenerSamples, "}, ",
#                                   "s1: {method: 'MCMC', samples: ",
#                                   s1Samples, "}}})", sep=""),
#                 inference_opts = list(method="MCMC", samples=listenerSamples),
#                 packages = c("node_modules/simpleCSV",
#                              "node_modules/babyparse"))
#     return(rs)
#   })
# }
# 
# setwd("../model")
# model_results = do.call(rbind,
#                         lapply(relevant_items,
#                                adjectivesModel(samples, samples)))
# setwd("../writeups/")
# 
# # write.csv(model_results,
# #           paste("../model/", priors_dir, "/",
# #                 "simulation-results/",
# #                 "model_results_alpha", alpha,
# #                 "_cost", cost,
# #                 "_", priors_dir,
# #                 samples/1000,
# #                 "K_",
# #                 model_commit, sep=""),
# #           row.names=F)
model_results = read.csv(paste("../model/", priors_dir, "/",
                               "simulation-results/",
                               "model_results_alpha", alpha,
                               "_cost", cost,
                               "_", priors_dir,
                               samples/1000,
                               "K_",
                               model_commit, sep=""))
```

```{r}
inductive = function(this_item, this_epsilon) {
  inductive_prob = sum((model_results %>% filter(item==this_item) %>%
                          mutate(new_item_cost = value - this_epsilon,
                                 inductive_true = new_item_cost > theta) %>%
                          filter(inductive_true))$prob)
  return(inductive_prob)
}

concrete = function(this_item, this_value) {
  concrete_prob = sum((model_results %>% filter(item==this_item) %>%
                         mutate(concrete_true = this_value > theta) %>%
                         filter(concrete_true))$prob)
  return(concrete_prob)
}
```

```{r}
modelvdata = d0 %>%
  filter(item %in% relevant_items) %>%
  mutate(item = factor(item)) %>%
  mutate(model = ifelse(qType=="inductive",
                        mapply(inductive, item, dollarAmt),
                        mapply(concrete, item, dollarAmt)))
```

```{r}
modelvdata %>%
  mutate(human = (response-1)/8) %>%
  gather("source", "rating", c(human, model)) %>%
  group_by(phrasing, source, item, qType, dollarAmt) %>%
  summarise(low = ci.low(rating),
            high = ci.high(rating),
            rating = mean(rating)) %>%
  as.data.frame() %>%
  ggplot(., aes(x=dollarAmt, y=rating, linetype=source, colour=item)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(x=dollarAmt, ymin=low, ymax=high), width=0) +
  scale_colour_brewer(type="qual", palette = 2) +
  facet_grid(qType ~ item, scale="free") +
  ylim(0,1)
```


