---
title: "Sorites Data Summary"
author: "Erin Bennett"
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{bayesnet}
output: html_document
---

```{r global_options, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = F, warning = F, cache = F, message = F,
                      sanitiz = F, fig.width = 5, fig.height = 3)
```

```{r load (and reformat) data}
source("utils.R")
source("reformatting_data.R")
df = load_sorites()
give_a_number = load_give_a_number()
prior_bins_data = load_priors()
```

# Experiments

## Wording used in sorites experiments

```{r load design descriptions}
sorites_designs = read.csv(data_dir( "/sorites/sorites_designs.csv"),
                           stringsAsFactors = F)
sorites_designs %>%
  select(-prompt, -left, -right, -concrete, -inductive) %>%
  rename(`inductive phrasing` = inductive_label) %>%
  pander(.,
       caption = "Sorites variations",
       align = rep("l", ncol(sorites_designs)))
lookup_phrasing = function(inductive_phrasing) {
  return((
    sorites_designs %>%
      filter(inductive_label == inductive_phrasing)
  )$inductive[[1]])
}
```

Possible phrasings of inductive premise:

* relative: "`r lookup_phrasing("relative")`"
* conditional: "`r lookup_phrasing("conditional")`"

Consistent across all experiments:

* Concrete premise: "`r sorites_designs$concrete[[1]]`"
* Prompt: "`r sorites_designs$prompt[[1]]`"
* Left (lower) label of likert scale: "`r sorites_designs$left[[1]]`""
* Right (higher) label of likert scale: "`r sorites_designs$right[[1]]`""

*In experiments 7a and 7b, phrasing was randomized between participants (either relative or conditional), but I did not record which phrasing was used for which participant

## Results of sorites experiments

The range of values asked about in the experiment affected responses a bit. For smaller ranges, participants gave higher responses for lower prices (that were at the top range within the experiment).


```{r}
RUN_AGG = T
## computing confidence intervals takes a long time.
## so just cache the results of this most of the time
if (RUN_AGG) {
  agg = df %>%
  group_by(id, qtype, phrasing, object, dollar_amount) %>%
  summarise(low = ci.low(response),
            high = ci.high(response),
            response = mean(response)) %>%
    ungroup
write.csv(agg, cache_dir("agg_cache.csv"), row.names = F)
}  else {
agg = read.csv(cache_dir("agg_cache.csv"))
}
agg = agg %>% mutate(phrasing = factor(phrasing))
```

```{r, fig.height=4, fig.width=12}
opacity = 0.5
agg %>% ggplot(., aes(x=dollar_amount, y=response, colour=id, group=id)) +
  geom_line(alpha=opacity) +
  geom_point(alpha=opacity) +
  # geom_line(alpha=opacity) +
  geom_errorbar(aes(ymin=low, ymax=high), width=0, alpha=opacity) +
  facet_grid(qtype~object, scale="free_x") +
  ylim(1, 9) +
  scale_colour_brewer(type="qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
agg %>% filter(qtype == "inductive") %>% group_by(object) %>%
  summarise(eps = min(dollar_amount),
         max = max(dollar_amount),
         nbins = max/eps)
```


## Priors experiments

### Give a number

I don't know Justine's exact phrasing for this, but participants were asked, for each item, a possible price for that item.

```{r, fig.height=2, fig.width=12}
give_a_number %>%
  ggplot(., aes(x=price, colour=object, fill=object)) +
  geom_density(alpha=1/2) +
  geom_histogram(bins=30) +
  facet_grid(~object, scales="free") +
  scale_colour_brewer(type="qual", palette = 6) +
  scale_fill_brewer(type="qual", palette = 6)
```


### Bins

Here are the instructions participants got in all of the prior experiments:

> In each scenario, someone has just bought an item. Please give your best estimate of the price of the item. You will do this by rating how likely you think it is that the actual price is within each of NBINS different ranges.
> 
> NAME bought a new *ITEM*.
> 
> Please rate how likely it is that the cost of the *ITEM* is within each of the following ranges.

```{r}
n_split = length(unique((prior_bins_data %>% filter(condition == "split"))$workerid))
```

There was a "split" condition (`r n_split` participants), where participants saw one bin at a time. In all other versions, the sliders for each item were shown together. We did not collect enough data in the split condition to normalize responses.

```{r}
RUN_AGG = T
if (RUN_AGG) {
  agg_bins = prior_bins_data %>%
    filter(condition!="split") %>%
    group_by(workerid, item, exp, condition) %>%
    mutate(
      slider_total = sum(rating),
      normed_rating = ifelse(slider_total==0, 0, rating / slider_total)) %>%
    group_by(item, condition, exp, UB, LB) %>%
    summarise(
      low = ci.low(normed_rating),
      high = ci.high(normed_rating),
      y = mean(normed_rating),
      x = (UB[[1]]+LB[[1]])/2) %>%
    ungroup %>% as.data.frame %>% mutate(group = paste(item, condition, exp))
  write.csv(agg_bins, cache_dir("agg_bins_cache.csv"), row.names=F)
} else {
  agg_bins = read.csv(cache_dir("agg_bins_cache.csv"))
}
agg_bins = agg_bins %>% rename(object=item)
```

```{r, fig.height=3, fig.width=12}
agg_bins %>%
  group_by(group) %>%
  mutate(y = y * length(y),
         low = low * length(y),
         high = high * length(y)) %>%
  ggplot(., aes(x,y, ymin=low, ymax=high, group=group, fill=object)) +
  geom_line(aes(colour=object), alpha=1/2) +
  geom_ribbon(alpha=1/5) +
  facet_wrap(~object, scale="free", ncol=5) +
  xlab("bin midpoint") +
  ylab("relative probability") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_brewer(type="qual", palette = 6) +
  scale_colour_brewer(type="qual", palette = 6) +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
```

