---
title: "Sorites Prior Elicitations"
author: "Erin Bennett"
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{bayesnet}
output: html_document
---

```{r global_options, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = F, warning = F, cache = F, message = F,
                      sanitiz = F, fig.width = 5, fig.height = 3)
```

```{r load_experiment_data_and_libraries, message=F, warning=F}
source("utils.R")
source("reformatting_data.R")
source("plot_model_results.R")
df = load_sorites()
give_a_number = load_give_a_number() %>%
  mutate(src = "data")
prior_bins = load_priors()
```

The adjectives model, used for the concrete premise relies on a prior distribution of prices for each object.

## Log-normal priors

### Give a number prior elicitation

```{r}
prior_giveanumber = plot_priors("../models/results/results-S1-5000_burn2500_lag10_giveanumber_chain1.csv")

draw_curves = function(mu, sigma, obj) {
  x = seq(0, get_obj_max(obj), length.out = 100)
  return(data.frame(
    x=x,
    density=dlnorm(x, meanlog=mu, sdlog=sigma)#*get_n_prices(obj)
  ))
}
# prior_giveanumber$fit %>%
#   group_by(object, variable) %>%
#   summarise(value = mean(value)) %>%
#   spread(variable, value) %>%
#   do(draw_curves(.$mu, .$sigma, .$object))
# ```
# 
# ```{r, fig.width=10, fig.height=2}
get_n_prices = function(obj) {
  give_a_number %>%
    group_by(object) %>%
    summarise(n = length(price)) %>%
    named_vec(object, n) %>%
    .[obj] %>%
    return()
}
draw_curves = function(mu, sigma, obj) {
  x = seq(0, get_obj_max(obj), length.out = 100)
  return(data.frame(
    x=x,
    density=dlnorm(x, meanlog=mu, sdlog=sigma)
  ) %>% mutate(
    prob = density/sum(density)*get_n_prices(obj)*10))
}
prior_fit = prior_giveanumber$fit %>%
  filter(result_type=="price_prior") %>%
  spread(variable, value) %>%
  group_by(object) %>%
  mutate(sigma = mean(sigma)) %>%
  group_by(object, sigma) %>%
  do(quantile_errorbars(.$mu)) %>%
  ungroup() %>%
  gather("region", "mu", c(y, ymin, ymax)) %>%
  group_by(object, region) %>%
  do(draw_curves(.$mu, .$sigma, .$object))
```

Prior prices (as measured by Justine's give_a_number study) are well fit by a log-normal distribution.

```{r, fig.width=10, fig.height=2}
prior_giveanumber$df %>%
  filter(src=="data") %>%
  ggplot() +
  geom_ribbon(data=prior_fit %>%
              select(-density) %>%
              spread(region, prob),
              aes(x=x, ymin=ymin, ymax=ymax),
              fill="black", alpha=1/3) +
  geom_line(data=prior_fit %>%
              select(-density) %>%
              spread(region, prob), aes(x=x, y=y),
            colour="black", alpha=1/2) +
  aes(x=price, colour=object, fill=object
      ) +
  # geom_density(alpha=1/3) +
  geom_histogram(alpha=1/3, bins=10) +
  facet_wrap(~object, ncol = 5, scales="free") +
  scale_color_brewer(type="qual", palette = 6) +
  scale_fill_brewer(type="qual", palette = 6) +
  ylab("Frequency") +
  xlab("Price")
ggsave("img/giveanumber_hist.png", width=15, height=3)
```

```{r, fig.width=10, fig.height=2}
prior_giveanumber$df %>%
  filter(src=="data") %>%
  ggplot() +
  geom_ribbon(data=prior_fit %>%
              select(-prob) %>%
              spread(region, density),
              aes(x=x, ymin=ymin, ymax=ymax),
              fill="black", alpha=1/3) +
  geom_line(data=prior_fit %>%
              select(-prob) %>%
              spread(region, density), aes(x=x, y=y),
            colour="black", alpha=1/2) +
  aes(x=price, colour=object, fill=object
      ) +
  geom_density(alpha=1/3) +
  # geom_histogram(alpha=1/3, bins=10) +
  facet_wrap(~object, ncol = 5, scales="free") +
  scale_color_brewer(type="qual", palette = 6) +
  scale_fill_brewer(type="qual", palette = 6) +
  ylab("Density") +
  xlab("Price")
ggsave("img/giveanumber_density.png", width=15, height=3)
```

The empirical CDFs between the posterior predictive and the actual data are highly correlated ($R^2 = `r round(prior_giveanumber[["R_squared"]], 3)`$).

```{r, fig.width=10, fig.height=2}
prior_giveanumber$df %>%
  group_by(src, object) %>%
  mutate(x = seq(1, max(price), length.out=length(price)),
         cdf = get_ecdf(price, x)) %>%
  do(get_ecdf_with_errorbars(.)) %>%
  ggplot() +
  aes(x=x, y=y, ymin=ymin, ymax=ymax,
      fill=src) +
  geom_ribbon(alpha=1/5) +
  geom_line(aes(color=src)) +
  facet_wrap(~object, scales="free",
             ncol=5) +
  scale_colour_solarized() +
  scale_fill_solarized() +
  ylab("Probability") +
  xlab("Price")
# print(prior_giveanumber$p)
ggsave("img/giveanumber_ecdf.png", width=15, height=3)
```

### Bins prior elicitations

The final bins prior elicitation, used to make the density plots in Noah's slides, is also well-fit by a lognormal distribution.

We assume that participants' responses are normally distributed around the true probability of the bin.

```{r}
# #### Fitting raw ratings
# 
# When we fit the raw resonses that participants gave on the sliders (without normalizing each distribution from each participant), the fit to raw responses is good.
# 
# ```{r}
# last_expt_bins_data_raw = prior_bins %>%
#   filter(exp=="12") %>%
#   group_by(workerid, object) %>%
#   # mutate(normed_response = rating/sum(rating)) %>%
#   ungroup() %>%
#   group_by(object, UB, LB) %>%
#   do(mean_cl_boot(.$rating)) %>%
#   # do(mean_cl_boot(.$rating)) %>%
#   ungroup()
# ```
# 
# ```{r}
# get_obj_max = function(obj) {
#   last_expt_bins_data_raw %>%
#     group_by(object) %>%
#     summarise(max_price = max(LB)) %>%
#     named_vec(object, max_price) %>%
#     .[obj] %>%
#     return()
# }
# draw_curves = function(mu, sigma, obj) {
#   last_expt_bins_data_raw %>%
#     ungroup() %>%
#     mutate(UB = ifelse(is.na(UB), Inf, num(UB))) %>%
#     mutate(prob = plnorm(UB, meanlog=mu, sdlog=sigma) - plnorm(LB, meanlog=mu, sdlog=sigma)) %>%
#     select(object, LB, prob) %>%
#     filter(object == obj) %>%
#     rename(x = LB) %>%
#     return()
# }
# 
# 
# last_expt_bins_fit =  read.csv(
#   "../models/results/results-prior-50000_burn25000_lag10_chain1.csv",
#   col.names = c("result_type", "variable",
#                 "IGNORE", "object",
#                 "value", "probability")) %>%
#   select(-IGNORE) %>%
#   filter(result_type == "price_prior") %>%
#   group_by(result_type, variable, object) %>%
#   mutate(sample = 1:length(value)) %>%
#   ungroup() %>%
#   filter(result_type=="price_prior") %>%
#   spread(variable, value) %>%
#   group_by(object) %>%
#   mutate(sigma = mean(sigma)) %>%
#   group_by(object, sigma) %>%
#   do(quantile_errorbars(.$mu)) %>%
#   ungroup() %>%
#   gather("region", "mu", c(y, ymin, ymax)) %>%
#   group_by(object, region) %>%
#   do(draw_curves(.$mu, .$sigma, char(.$object)))
# ```
# 
# 
# ```{r, fig.width=15, fig.height=6}
# nbins = last_expt_bins_data %>%
#   group_by(object) %>%
#   summarise(N = length(unique(LB))) %>%
#   named_vec(object, N)
# last_expt_bins_comparison = last_expt_bins_fit %>%
#   select(object, region, x, prob) %>%
#   mutate(prob = prob) %>%
#   mutate(src="model") %>%
#   ungroup() %>%
#   rbind(last_expt_bins_data_raw %>%
#           rename(x = LB) %>%
#           select(-UB) %>%
#           gather("region", "prob", c(y, ymin, ymax)) %>%
#           mutate(src="data"))
# last_expt_bins_comparison %>%
#   group_by(object, src, region) %>%
#   # mutate(prob = prob/max(prob)) %>%
#   filter(x != max(x)) %>%
#   ungroup() %>%
#   spread(region, prob) %>%
#   ggplot() +
#   aes(x=x, y=y, ymin=ymin, ymax=ymax, fill=object, linetype=src) +
#   geom_ribbon(alpha=1/2) +
#   geom_line(aes(colour=object)) +
#   facet_wrap(src~object, ncol = 5, scales="free") +
#   scale_fill_brewer(type="qual", palette = 6) +
#   scale_colour_brewer(type="qual", palette = 6)
# ggsave("img/last_bins_fit_raw.png", width=15, height=6)
# ```
# 
# ```{r}
# sum_lower = function(df) {
#   df$prob = mapply(function(p, x) {
#     sum(df$prob[df$x < x]) %>% return()
#   }, df$prob, df$x)
#   return(df)
# }
# 
# bins_r_squared = last_expt_bins_comparison %>%
#   group_by(object, region, src) %>%
#   do(sum_lower(.)) %>%
#   filter(region=="y") %>%
#   spread(src, prob) %>%
#   with(cor(model, data)^2)
# ```
# 
# The CDFs computed from the last prior elicitation and its lognormal fit are highly correlated ($R^2 = `r round(bins_r_squared, 3)`$).
# 
# ```{r, fig.width=15, fig.height=3}
# last_expt_bins_comparison %>%
#   group_by(object, region, src) %>%
#   do(sum_lower(.)) %>%
#   spread(region, prob) %>%
#   ggplot(aes(x=x, y=y, ymin=ymin, ymax=ymax,
#              fill=src)) +
#   geom_line(aes(colour=src)) +
#   geom_ribbon(alpha=1/5) +
#   facet_wrap(~object, ncol = 5, scales="free") +
#   scale_colour_solarized() +
#   scale_fill_solarized() +
#   geom_hline(yintercept = 1, linetype="dashed", colour="black", alpha=1/5)
# ggsave("img/last_bins_ecdf.png", width=15, height=3)
```

We first normalize slider ratings within each participant and each object so that they form a probability distribution. We then fit to a lognormal distribution.

```{r}
last_expt_bins_data = prior_bins %>%
  filter(exp=="12") %>%
  group_by(workerid, object) %>%
  mutate(normed_response = rating/sum(rating)) %>%
  ungroup() %>%
  group_by(object, UB, LB) %>%
  do(mean_cl_boot(.$normed_response)) %>%
  # do(mean_cl_boot(.$rating)) %>%
  ungroup()
```

```{r}
get_obj_max = function(obj) {
  last_expt_bins_data %>%
    group_by(object) %>%
    summarise(max_price = max(LB)) %>%
    named_vec(object, max_price) %>%
    .[obj] %>%
    return()
}
draw_curves = function(mu, sigma, obj) {
  last_expt_bins_data %>%
    ungroup() %>%
    mutate(UB = ifelse(is.na(UB), Inf, num(UB))) %>%
    mutate(prob = plnorm(UB, meanlog=mu, sdlog=sigma) - plnorm(LB, meanlog=mu, sdlog=sigma)) %>%
    # mutate(prob = prob / sum(prob)) %>%
    select(object, LB, prob) %>%
    filter(object == obj) %>%
    rename(x = LB) %>%
    return()
}


last_expt_bins_fit =  read.csv(
  #"../models/results/results-prior-50000_burn25000_lag10_chain1.csv",
  # "../models/results/results-S1-50_burn25_lag1_chain1_bins_all_listener1normed_rating_ignore_last_bin.csv",
  # "../models/results/results-prior-50000_burn25000_lag10_chain1_normed_rating_ignore_last_bin.csv", # 77minutes
  # "../models/results/results-prior-10000_burn5000_lag20_chain2_normed_rating_ignore_last_bin.csv", # 6 minutes
  "../models/results/results-prior-50000_burn25000_lag10_chain1_normed_rating_ignore_last_bin.csv",
  col.names = c("result_type", "variable",
                "IGNORE", "object",
                "value", "probability")) %>%
  select(-IGNORE) %>%
  filter(result_type == "price_prior") %>%
  group_by(result_type, variable, object) %>%
  mutate(sample = 1:length(value)) %>%
  ungroup() %>%
  filter(result_type=="price_prior") %>%
  spread(variable, value) %>%
  group_by(object) %>%
  mutate(sigma = mean(sigma)) %>%
  group_by(object, sigma) %>%
  do(quantile_errorbars(.$mu)) %>%
  ungroup() %>%
  gather("region", "mu", c(y, ymin, ymax)) %>%
  group_by(object, region) %>%
  do(draw_curves(.$mu, .$sigma, char(.$object)))
```


```{r, fig.width=15, fig.height=3}
nbins = last_expt_bins_data %>%
  group_by(object) %>%
  summarise(N = length(unique(LB))) %>%
  named_vec(object, N)
last_expt_bins_comparison = last_expt_bins_fit %>%
  select(object, region, x, prob) %>%
  mutate(src="model") %>%
  ungroup() %>%
  rbind(last_expt_bins_data %>%
          rename(x = LB) %>%
          select(-UB) %>%
          gather("region", "prob", c(y, ymin, ymax)) %>%
          mutate(src="data"))
last_expt_bins_comparison %>%
  group_by(object, src, region) %>%
  # mutate(prob = prob/max(prob)) %>%
  filter(x != max(x)) %>%
  ungroup() %>%
  spread(region, prob) %>%
  ggplot() +
  aes(x=x, y=y, ymin=ymin, ymax=ymax, fill=object, linetype=src) +
  geom_ribbon(alpha=1/2) +
  geom_line(aes(colour=object)) +
  facet_wrap(~object, ncol = 5, scales="free") +
  scale_fill_brewer(type="qual", palette = 6) +
  scale_colour_brewer(type="qual", palette = 6) +
  ylab("Normalized slider ratings") +
  xlab("Price range lower bound")
ggsave("img/last_bins_fit.png", width=15, height=3)
```

```{r}
sum_lower = function(df) {
  df$prob = mapply(function(p, x) {
    sum(df$prob[df$x < x]) %>% return()
  }, df$prob, df$x)
  return(df)
}

bins_r_squared = last_expt_bins_comparison %>%
  group_by(object, region, src) %>%
  do(sum_lower(.)) %>%
  filter(region=="y") %>%
  spread(src, prob) %>%
  with(cor(model, data)^2)
```

The CDFs computed from the last prior elicitation and its lognormal fit are highly correlated ($R^2 = `r round(bins_r_squared, 3)`$).

```{r, fig.width=15, fig.height=3}
last_expt_bins_comparison %>%
  group_by(object, region, src) %>%
  do(sum_lower(.)) %>%
  spread(region, prob) %>%
  ggplot(aes(x=x, y=y, ymin=ymin, ymax=ymax,
             fill=src)) +
  geom_line(aes(colour=src)) +
  geom_ribbon(alpha=1/5) +
  facet_wrap(~object, ncol = 5, scales="free") +
  scale_colour_solarized() +
  scale_fill_solarized() +
  geom_hline(yintercept = 1, linetype="dashed", colour="black", alpha=1/5) +
  ylab("Probability") +
  xlab("Price")
ggsave("img/last_bins_ecdf.png", width=15, height=3)
```

### Comparing elicitations

Although both prior elicitations are well fit by lognormal distributions, the distributions are very, very different from each other.

```{r, fig.width=15, fig.height=3}
last_expt_bins_comparison %>%
  filter(src=="data") %>%
  mutate(expt = "last_bins") %>%
  group_by(object, region, src, expt) %>%
  do(sum_lower(.)) %>%
  ungroup() %>%
  spread(region, prob) %>%
  rbind(
    prior_giveanumber$df %>%
      filter(src=="data") %>%
      mutate(expt = "giveanumber") %>%
      group_by(src, object) %>%
      mutate(x = seq(1,
                     # max(price),
                     get_obj_max(object[[1]]),
                     length.out=length(price))) %>%
      do(get_ecdf_with_errorbars(.)) %>%
      ungroup() %>%
      select(-price)) %>%
  ggplot(aes(x=x, y=y, ymin=ymin, ymax=ymax,
             fill=expt)) +
  geom_line(aes(colour=expt)) +
  geom_ribbon(alpha=1/5) +
  facet_wrap(~object, ncol = 5, scales="free") +
  scale_colour_brewer(type="qual", palette = 1) +
  scale_fill_brewer(type="qual", palette = 1) +
  ylab("Probability") +
  xlab("Price")
ggsave("img/prior_expts_ecdf.png", width=15, height=3)
```

```{r}
read.csv(
  #"../models/results/results-prior-50000_burn25000_lag10_chain1.csv",
  # "../models/results/results-S1-50_burn25_lag1_chain1_bins_all_listener1normed_rating_ignore_last_bin.csv",
  # "../models/results/results-prior-50000_burn25000_lag10_chain1_normed_rating_ignore_last_bin.csv", # 77minutes
  "../models/results/results-prior-10000_burn5000_lag20_chain2_normed_rating_ignore_last_bin.csv", # 6 minutes
  col.names = c("result_type", "variable",
                "IGNORE", "object",
                "value", "probability")) %>%
  select(-IGNORE) %>%
  filter(variable %in% c("sigbin", "mu", "sigma")) %>%
  unite("variable", variable, object) %>%
  mutate(variable = ifelse(variable=="sigbin_NA", "sigbin", variable)) %>%
  ggplot(aes(x=value)) +
  geom_histogram(bins=30) +
  facet_wrap(~variable, scales="free")
```

